Interisland movements and oceanic swimming of woodland caribou in Newfoundland

### 2020-05-11 paper/manuscript.Rmd
question 2 and 3

1) How does the energetic cost or risk of swimming differ from walking on sea
ice? The cost of swimming may be lower than the risk of falling through sea ice
and drowning, so what proportion of inter-island movements are swimming events
compared to walking on ice? Although we are unable to

2) At which varying temporal and ecological scale do caribou choose to swim
between islands? Does the time of day, weather, seasonal trends, or availability
of food influence swimming?

3) Does reproductive status (presence of a calf-at-heel) or demographics (age,
sex) influence propensity for oceanic swimming? Our initial observation was of
an adult male, but the only collared individuals are adult females. Are younger
animals more likely to swim if they are outcompeted? More likely? Are males more
likely when in the summer their only concern is foraging, given the relatively
minimal predation risk they face without calves?

>>>>

1) How does the energetic cost or risk of swimming differ from walking on sea
ice? The cost of swimming may be lower than the risk of falling through sea ice
and drowning, so what proportion of inter-island movements are swimming events
compared to walking on ice? The presence and extent of sea ice varies annually
in our study area, and although we are unable to determine the exact timing or
duation of sea ice, we delineate on Figure 2b the timing of typical sea ice
arrival and departure.

2) At which temporal and spatial scales do caribou choose to swim
between islands? Does the time of day, weather, season, or availability
of food influence swimming?

3) Does reproductive status (presence of a calf-at-heel) or demographic class (age,
sex) influence propensity for oceanic swimming? Our initial observation was of
an adult male, but all collared individuals were adult females. Are younger
caribou more likely to swim due to heightened competition? Are males more
likely to swim in the summer given the are not restricted based on presence of a calf-at-heel, as females are.
